Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-04-05 manuscript/manuscript.tex
Modified linear density in manuscript

>>>>

In order to perform the comparison, we proposed a thin and a thick 
spherical shells with 1km and 35km of thickness, respectively, whose 
outer radii is equal to the mean Earth radius.
On both cases we will suppose that the density assumes a value of 
2670~kg/m$^3$ on the outer surface and 3300~kg/m$^3$ at the inner 
radius:

Then we computed the percentage difference between the numerical model 
with its corresponding analytical solution (equation 
\ref{eq:density-linear}) for the thick and the thin spherical shell.
